\begin{multicols}{2}
\fontsize{14}{1.5}\selectfont
\textbf{Ingredients:} 
\begin{itemize}
\setlength{\itemsep}{20pt}
\item 2 cups flour
\item 3 eggs (room temperature)  
\item $1\frac{1}{4}$ cup white sugar 
\item 1 stick unsalted butter (softened)
\item $\frac{1}{2}$ cup milk (room temperature)
\item $\frac{1}{2}$ cup lemon juice 
\item 1 teaspoon baking powder
\item 1 tablespoon lemon zest
\item $\frac{1}{2}$ teaspoon baking soda 
\item $\frac{1}{4}$ teaspoon salt




\end{itemize}


\columnbreak
\textbf{Procedure:}
\medskip


\begin{enumerate}
\item Preheat the oven to 350 degrees. 


\medskip
\item Grease and flour (or use non-stick spray) a 9 x 5 inch loaf pan.
\medskip

\item Sift together flour, baking powder, soda, and salt. Stir in lemon zest. Set aside.


\item In a large mixing bowl or stand mixer beat butter on medium speed for 2-3 minutes.
\medskip 
\item Gradually add the sugar and continue beating for another 2-3 minutes.
\medskip 
\item Add eggs, one at a time. Make sure you scrape the bottom of your bowl.
\medskip
\item Add lemon juice (the batter will curdle).
\medskip
\item Alternate addition of flour and milk (in 2 additions). Mix on low speed until combined. Do not over mix.
\medskip
\item Bake in preheated oven for 60-75 minutes until golden and cake tester comes out clean.
\medskip
\item Transfer pan to a rack where it can cool down for about 10 minutes before removing loaf to cool down completely on a wire rack.
\medskip \item \textbf{To make icing:} whisk about a quarter cup of lemon juice adding powdered sugar until mixture thickens to a honey-like consistency. Drizzle over a slice for maximum lemon flavor! 
\end{enumerate}

\end{multicols}