\begin{multicols}{2}
\fontsize{14}{1.5}\selectfont
\textbf{Ingredients:}
\begin{itemize}
\setlength{\itemsep}{20pt}
\item 1 lb white mushrooms
\item $1\frac{1}{2}$ cups arborio rice
\item 10 oz. grape tomatoes
\item 1 yellow onion
\item $\frac{1}{2}$ cup parmesan cheese
\item 1 tbsp. olive oil
\item 2 tbsp. butter
\item 4 cups vegetable or chicken broth (1 box)
\item 5 cloves of garlic
\item Salt to taste
\item $2$ tsp. dried thyme
\item green onions (optional garnish)
\end{itemize}


\columnbreak
\textbf{Procedure:}
\medskip


\begin{enumerate}

\item Slice the mushrooms and put on medium heat in a large pan with a pinch of salt. Cook until mushrooms release their water and let the water boil off while stirring occasionally. When the water is mostly boiled off, remove the mushrooms and set aside. 
\item Add one box of chicken stock to a medium saucepan and bring to a boil. Once boiling, reduce to a simmer. 
\item Add a diced onion to a large pan with a tablespoon of olive oil and cook until slightly softened. 
\item When the onions are softened, add garlic, rice, and 1 tbsp. butter. Cook on medium heat for a couple of minutes, until the garlic is fragrant. 
\item Reduce heat to medium-low. Adding about $\frac{1}{2}$ cup at a time, add chicken stock to the rice. When the rice has absorbed the stock, add more. Repeat until about $\frac{1}{4}$ of the chicken stock remains. Add water if there is no more chicken stock and the rice is not yet cooked. 
\item Add halved grape tomatoes to the pan and continue adding chicken stock.
\item Once the rice is cooked, add the mushrooms back in, along with 1 tbsp butter, and stir in about $\frac{1}{2}$ cup of parmesan cheese. Once the cheese melts and everything is combined, remove from heat. 
\item Season with salt and thyme to taste. Garnish with chopped green onions on top, if desired. 


 
\end{enumerate}
\end{multicols}
