\begin{multicols}{2}
\textbf{Ingredients:}
\begin{itemize}
\item $\frac{1}{2}$ lb rigatoni
\item $\frac{1}{2}$ medium yellow onion, diced finely 
\item $\frac{1}{2}$ lb Italian sausage - ground is fine but if you're using links, remove from the casings 
\item 1 28-oz can crushed tomatoes 
\item $\frac{1}{2}$ cup heavy cream
\item 6 oz mozarella, shredded  
\item $\frac{1}{2}$ cup shredded parmesan 
\item 4 large cloves of garlic 
\item 2 tsp basil leaves
\item 1 tsp oregano
\item 1 tsp dried thyme 
\item $\frac{1}{2}$ tsp crushed fennel seed 
\item 1 tsp red pepper flakes 



\end{itemize}


\columnbreak
\textbf{Procedure:}
\medskip


\begin{enumerate}
\item Preheat the oven to 400° F. Add the pasta to a medium bowl and cover with hot water. Add a pinch of salt. Set aside while you make the sauce.
\item Heat a large skillet over medium heat and add a little olive oil. Add the diced onions, sausage, crushed red pepper flakes, fennel, and thyme along with a generous pinch of salt. Saute, stirring occasionally and breaking up the sausage into bite-sized bits, until the onions are translucent and the sausage is browned in spots.
\item Add the garlic and saute until fragrant, about 30 seconds. Add the tomatoes and bring to a simmer and cook for about 10 minutes. Stir in the heavy cream.  
\item Drain the pasta and add it to the sauce. Stir.

\item Add about half of the pasta and sauce to a 9" square baking dish. Grate parmesan over the pasta in a thin layer. Add about half of the mozzarella over the pasta in an even layer. Repeat with the remaining pasta and cheese.

\item Bake until the cheese is browned in spots and the sauce is bubbling, about 20 minutes. Let cool for 10 minutes before serving.  


\end{enumerate}
\end{multicols}