\begin{multicols}{2}
\fontsize{14}{1.5}\selectfont
\textbf{Ingredients:}
\begin{itemize}
\item 6 lemons
\item 2 cups heavy cream
\item $\frac{2}{3}$ cup of white sugar
\item zest of 1 lemon 



\end{itemize}


\columnbreak
\textbf{Procedure:}
\medskip


\begin{enumerate}
\item Note: You'll need to reduce to 2 cups of liquid, you can estimate this by pouring two cups of water into the saucepan you plan to use then take a wooden skewer or chopstick and put it in the water. Mark the level of the water on the skewer.
\item Note: One of the lemons is for zesting, you can empty it out for presentation but it will not be as pretty as the others. 
\item Cut lemons in half vertically and use a spoon to scoop out the insides into a medium bowl. Keep this as you will need the juice. 
\item In a medium (preferably deep) saucepan, combine cream, sugar and lemon zest. Bring to a boil over medium heat and cook, stirring frequently, to dissolve the sugar.  Don't walk away from the mixture as it can easily boil over and it will be \textit{incredibly} sticky. If it gets close to the top, remove the pan briefly from the heat to slow the boil.

\item Cook until the mixture reduces to two cups (see first note). Remove from the heat and add the lemon juice. Set the saucepan aside to cool until a skin forms on top, about 20 minutes. Strain the posset through a fine mesh strainer into a bowl. Discard the lemon zest.

\item Divide the mixture between the lemon halves or serving bowls. Refrigerate, uncovered, until set, about 2-3 hours. Once fully chilled, cover with plastic wrap and refrigerate for up to 2 days.  


\end{enumerate}
\end{multicols}